Experiments with Synthetic Data

### 2022-07-20 dev/notebooks/synthetic.qmd
some more progress on experiment setup

@@

```{julia}
# Variables:
μ = 0.1
γ = 0.75
n_rounds = 2
n_folds = 5
T = 1000
```

```{julia}
output = run_experiment(experiment; n_rounds=n_rounds, μ=μ, n_folds=n_folds, γ=γ, T=T)
```

```{julia}
using CSV, BSON
CSV.write(joinpath(output_path,"synthetic_data.csv"), output)
BSON.@save joinpath(output_path,"synthetic_data.bson") output
```

>>>>

```{julia}
# Models:
models = (Bayesian=M_laplace, Plugin=M)
# Generators:
loss = :logitbinarycrossentropy
generators = (
    Greedy=GreedyGenerator(loss=loss), 
    Generic=GenericGenerator(loss=loss),
    REVISE=REVISEGenerator(loss=loss)
)
```

@@

```{julia}
# Variables:
μ = 0.1
γ = 0.75
n_rounds = 10
n_folds = 5
T = 1000
```

```{julia}
output = run_experiment(experiment; n_rounds=n_rounds, μ=μ, n_folds=n_folds, γ=γ, T=T)
using CSV, BSON
CSV.write(joinpath(output_path,"synthetic_data.csv"), output)
BSON.@save joinpath(output_path,"synthetic_data.bson") output
```
